---
title: "Graphics with ggplot2"
---


The ggplot2 package was created by Hadley Wickham. It can be uased to draw complex plots with R.

<h1>Why ggplot2?</h1>

Here are some advantages of using ggplot2:

1. Consistent underlying grammar of graphics 

2. Plot specification at a high level of abstraction

3. Flexibility

4. Theme system for polishing plot appearance

Some things you cannot do with ggplot2:

1. 3-dimensional graphics

2. Interactive graphics


<h2>Scatterplot</h2>

```{r,message=F, warning=F}
library(mosaic) 
library(ggplot2) 
```

```{r}
g<-ggplot(data=RailTrail,aes(x=volume,y=hightemp))+ # specify x and y data
  
geom_point(aes(color = precip), size = 3)+ #fill points according to amount of a variable and adjust point size

guides(color=guide_legend(title="Amount of precipitation"))+ # title of the legend
  
ggtitle('Scatterplot ') + # title of the plot 
  
theme(axis.text=element_text(size=16), #themes of x and y axis
axis.title=element_text(size=20),
plot.title=element_text(size = 24)) +
  
ylab('High temperature')+xlab('Number of crossings per day')  #title of x and y axis


g
```

<h2>Bar Graphs</h2>
```{r}

p <- ggplot(data = Marriage, aes(x = race))+ #specify data 
  
geom_bar(aes(fill = prevconc), position = 'fill') + # fill each bar according to amount of another variable "prevconc"

  guides (fill = guide_legend(title = "The way last marriage ended"))+  # title of the legend
  ggtitle('Barplot of % difference in each race') + 

  theme(axis.text=element_text(size=14),# text sizes of aixs titles
  axis.title=element_text(size=20),
  plot.title=element_text(size = 22)) +

  ylab('Percent')+xlab('Race')+ # aixs titles
  
  coord_flip()  #flip the graph to horizontal bar graph
     

p
```




Reference
[Reference 1](https://tutorials.iq.harvard.edu/R/Rgraphics/Rgraphics.html).